\section{Reading guide}
The report is expected to be read in chronological order. 

It contains extensive use of symbols and abbreviations. A list of both including short descriptions can be found in section \ref{sec:symbol_list} and \ref{sec:abbreviation_list} respectively. 

The report is written expecting the reader to have knowledge about power electronics, control theory and embedded systems.

\medskip
The report has the following sections:

\medskip
\emph{Section \ref{sec:introduction} - Introduction} gives a short introduction to the project and outlines a set of system requirements.

\medskip
\emph{Section \ref{sec:hardware} - Hardware} goes through the component selection, circuit and PCB design of the analog board and its handling of the analog signals, the power board's handling of the power components, the driver board's handling the control of the power board depending on signals from the embedded system.

\medskip
\emph{Section \ref{sec:control} - Control} contains the modeling of the system, as well as the design of a suitable controller. 

\medskip
\emph{Section \ref{sec:embedded_system} - Embedded system} contains descriptions of all elements implemented in the embedded system. These include the logic on the FPGA as well as functionality implemented on the processing system. 

\medskip
\emph{Section \ref{sec:discussion} - Discussion} goes through the interpretation of the test results, some possible problems with the design and explains how the design relates to the requirements found in section \ref{sec:introduction}.

\medskip
\emph{Section \ref{sec:conclusion} - Conclusion} outlines how the designed system fulfills the requirements.

\medskip
\emph{Section \ref{sec:symbol_list} - Symbol list} contains a list of all symbols together with a short description.

\medskip
\emph{Section \ref{sec:abbreviation_list} - Abbreviation list} contains a list of all abbreviations together with a short description.

\medskip
\emph{Section \ref{sec:references} - References} contains a list of the sources used.


\medskip
\emph{Section \ref{sec:appendix} - Appendix} 

\quad \textit{Appendix \ref{app:code_samples} - Code samples} contains a selection of the most important and interesting pieces of code.

\quad \textit{Appendix \ref{app:component_list} - Component List} contains a list of components for each board.

\quad \textit{Appendix \ref{app:schematics} - Schematics} contains all circuit designs made in the project.

\quad \textit{Appendix \ref{app:pcb_layout} - PCB Layout} contains pictures of all PCB designed. 

