
\section{Embedded system}
\label{sec:embedded_system}
The embedded system's task is to handle the control for the inverter.

The section is divided into three subsections. First the overall system architecture, then the low-level drivers implemented in the FPGA part of the controller and lastly the processing system and interface with a computer. 




% Software structure
\input{sections/software/ps/software_structure.tex}

%%%%%%%%%%%%%%%%%%%%% PL %%%%%%%%%%%%%%%%%%%%%
\subsection{Programmable Logic (PL)}
To take advantage of the parallel and super fast nature of FPGA logic all the low-level drivers are placed in logic. The section will go through the development and use of the modules used which includes a PWM module, an encoder module and an ADC module.

% PWM generator
\input{sections/software/pl/pwm.tex}

% Encoder
\input{sections/software/pl/encoder.tex}

%ADC
\input{sections/software/pl/adc.tex}

\subsubsection*{Subconclusions}
A dual PWM module is developed that can produce two individual and inverted PWM signals with dead time and ADC trigger pulses. Tests show that three of these modules can be used at the same time phase shifted $120^\circ$. The encoder module IP is included and a higher level algorithm is developed to improve the readings. Lastly the ADC's are configured and linked to the data pins, trigger and an interrupt is set up.

%%%%%%%%%%%%%%%%%%%%% PS %%%%%%%%%%%%%%%%%%%%%
\subsection{Processing System (PS)}
All the high level control and communication is placed on the processing system to get the benefit of higher abstraction on a processor. The section is structured in the same way as data is processed. First the ISR and how the PL triggers the PS, then the FOC and lastly how the result is transferred back to the PL. The section will end with the communication interface between the embedded system and a computer.


% Interrupt Service Routine ISR
\input{sections/software/ps/ISR.tex}

% Clarke Park
\input{sections/software/ps/clarkepark.tex}

% Controller
\input{sections/software/ps/controller.tex}

% Communication between PL and PS
\input{sections/software/ps/communication_to_pl.tex}

% Computer inteface
\input{sections/software/ps/uart.tex}

\subsubsection*{Subconclusion}
A short ISR is developed to simply trigger the actual control loop in the processor. When the control is triggered it runs Clarke and Park Transformations, angle interpolation, and two PI controllers. The controller output is then converted back into PWM thresholds with an Inverse Park and Inverse Clarke transformation and the result is put into block RAM for the PL to use.

